---
title: "`r params$disease`: Stratified report of signals"
subtitle: "This report uses `r params$disease` cases reported in `r params$country` (`r params$indicator`)"
date: "Generated on:  `r format(Sys.time(), '%Y-%m-%d')`"
output:
  html_document:
    css: "style.css"
    number_sections: true
    theme: united
    toc: true
    toc_depth: 3
    toc_float: true
params:
  file : NULL
  disease: "Salmonellosis"
  country: "EU-EEA - complete series"
  indicator: "Reported cases"
  stratification: "Confirmed cases"
  unit: "Month"
  daterange: !r c("2011-01-01", "2016-12-31")
  algo: "FarringtonFlexible"
  testingperiod: !r 3
  tempPath: !r tempdir()
---





```{r Config, echo = FALSE, results = 'hide', warning = FALSE, message = FALSE}


##******************************************************************************
## Chunk options
##******************************************************************************

knitr::opts_chunk$set(eval=TRUE, echo=FALSE, 
               fig.align='center',fig.width=13,fig.height=5,
               message=FALSE, warning=FALSE)

knitr::knit_hooks$set(inline = function(x) {
  format(x, big.mark=",")
})


##******************************************************************************
## Definition of the main color of graphs and table
##******************************************************************************

maincolor="#69AE23"


##******************************************************************************
## Libraries
##******************************************************************************

library(ggplot2)
library(dplyr)

```





```{r Parameters}

## ~~~~~~~~~~~~~~~~
## Setting parameters
## ~~~~~~~~~~~~~~~~

if(is.null(params$file)) {
  dataset <- EpiSignalDetection::SignalData
} else {
  inFile <- params$file
  dataset <- EpiSignalDetection::importAtlasExport(inFile$datapath)
  dataset <- EpiSignalDetection::cleanAtlasExport(dataset)
}

input <- list(
  disease = params$disease,
  country = params$country,
  indicator = params$indicator,
  unit = params$unit,
  daterange = params$daterange,
  algo = params$algo,
  testingperiod = params$testingperiod
)

tempPath <- params$tempPath

#--- Filtering on country, stratification and time unit
dataset <- EpiSignalDetection::filterAtlasExport(dataset, input, stratified = TRUE)

```





```{r StudyPeriodDefinition}

#--- Defining the study period
StudyPeriod <- EpiSignalDetection::studyPeriod(input)

#--- Defining the testing period period
TestingPeriod <- StudyPeriod$Time[length(StudyPeriod$Time):(length(StudyPeriod$Time) 
                                                            - input$testingperiod + 1)]
```





```{r GapsDefinition}

#-- Excluding countries with gaps and EU pre-computed values from the TS
excluded <- unique(dataset$RegionName[ is.na(dataset$NumValue) ])

if (input$country == "EU-EEA - complete series") {
  included <- unique(dataset$RegionName[!(dataset$RegionName %in% c(excluded, "EU", "EU/EEA"))])
  if (length(included) != 0) {
    dataset <- dplyr::filter(dataset, dataset$RegionName %in% included )
  } else {
    warning("All countries present with at least one gmissing value in the time series")
  }
} else if (length(excluded) !=0) {
  warning("The selected country presents with at least one missing value in the time series")
}


#-- Dataset for the testing period (TP) only
datasetTP <- dplyr::filter(dataset, Time %in% TestingPeriod)

```





# Study period: `r StudyPeriod$Time[1]` to `r StudyPeriod$Time[length(StudyPeriod$Time)]`
* __Historical data__: From `r StudyPeriod$Time[1]` 
to `r StudyPeriod$Time[length(StudyPeriod$Time) - input$testingperiod]`.
* __signal detection period__: 
The last `r input$testingperiod` `r tolower(input$unit)`(s) 
of the study period: from `r TestingPeriod[input$testingperiod]` 
to  `r TestingPeriod[1]`.
* __Time unit__: `r input$unit`(s). 
* __Signal detection algorithm__: `r input$algo`.
* __Gaps in the time series__: `r ifelse(input$country == "EU-EEA - complete series", (ifelse(length(excluded) !=0, paste("The following country(ies) presented with at least one missing value in the time series:", paste(excluded, collapse = ", ")), "None" )), (ifelse(length(excluded) !=0, "The selected country presented with at least one missing value in the time series", "None" )))`.





# Overview cases reported in the signal detection period: `r TestingPeriod[input$testingperiod]` to `r TestingPeriod[1]`


* There is(are) `r length(unique(datasetTP$RegionName[datasetTP$NumValue>0]))` 
country(ies) reporting at least 1 case in the signal detection period.
* There are `r sum(datasetTP$NumValue, na.rm=TRUE)` cases reported 
in the signal detection period, all strata added up.


```{r GraphByReportingCountries}

if(input$country == "EU-EEA - complete series") {
  
  datasetByCountry <- datasetTP %>%
    dplyr::group_by_( c("RegionName") ) %>%
    dplyr::summarise( NumValue = sum(NumValue)  ) %>%
    dplyr::ungroup()
  
  
  #--- Sort by number cases by countries 
  datasetByCountry <- datasetByCountry %>%
    dplyr::arrange(NumValue) %>%
    dplyr::mutate(RegionName = factor(datasetByCountry$RegionName, levels = datasetByCountry$RegionName))

  
  p <- ggplot(datasetByCountry, aes(x = RegionName, y = NumValue)) +
    geom_bar(stat = "identity", fill = maincolor) +
    scale_y_continuous(expand = c(0,0)) +
    coord_flip() +
    labs(title = "Graph: Number of cases observed by country in the signal detection period", 
         x = "Reporting country", y = "Number of cases") +
    theme(title = element_text(size = 14), 
          axis.text = element_text(size = 12),
          axis.text.x = element_text(size = 12),
          axis.title = element_text(size = 14, face = "bold"), 
          plot.title = element_text(color = "grey", hjust = 0, vjust = 0),
          panel.grid.major = element_blank(), 
          panel.grid.minor = element_blank()) 
  p
}

```





# Stratification variable

This report is stratified according to the data entered in the variable 'Population'.



```{r}
strata <- na.omit(unique(datasetTP$Population[datasetTP$NumValue>0]))

```


* The selected strata are those with at least one reported case during 
the signal detection period.
* There are `r length(strata)` strata with at least one case 
in the signal detection period: `r paste(strata, collapse = ", ")`.

In decreasing order of number of cases, the most frequent serotypes on 
the signal detecion period are:


```{r TableByStratum}
tab <- tapply(datasetTP$NumValue, datasetTP$Population, sum)
tab <- as.data.frame(tab)
names(tab) <- "Number of cases"

DT::datatable(tab, 
              options = list(
                pageLength = 20,
                autoWidth = FALSE,
                dom = 't',
                order = list(list(1, 'desc')),
                columnDefs = list(
                  list(className = 'dt-left', orderable = TRUE, targets = 1))),
              caption = "Table: Number of cases by stratum")

``` 





# Signal detection: `r TestingPeriod[input$testingperiod]` to `r TestingPeriod[1]`


<a name="result_tables"></a>


```{r LoopByCountry, results = 'hide', fig.show = 'hide'}

#--- Preparation of the result table that will be append through the following loop
Result <- data.frame( Time = "" ,  
                      Place = "" , 
                      Stratum = "",
                      Observed = "" ,
                      Threshold.ALGO = "", 
                      ALGO = "", 
                      Ranking = NA,
                      p.value = "",
                      stringsAsFactors=FALSE)


#-- Creation of a EU/EEA
if(input$country == "EU-EEA - complete series"){
  datasetEU <- dataset %>%
    dplyr::group_by_("StudyPeriod", "Population" ) %>%
    dplyr::summarise( NumValue = sum(NumValue)  ) %>%
    dplyr::ungroup()
  datasetEU <- data.frame(RegionName = "EU-EEA - complete series", datasetEU)
  dataset <- dataset[, c("RegionName", "Population", "StudyPeriod", "NumValue")]
  dataset <- rbind(datasetEU, dataset)
}

out <- NULL

#-- Creation of stratification levels
countries <- na.omit(unique(dataset$RegionName))

for(i in 1:length(countries)){
  country = countries[i]
  
  for(j in 1:length(strata)){
    stratum = strata[j]
    
    dataset_1 = dplyr::filter(dataset, 
                              RegionName == country & Population == stratum)
    
    if(nrow(dataset_1) != 0) {
      
      #-------------------------------------------------------
      #---- Sts object
      #-------------------------------------------------------
      
      dataset.sts <- EpiSignalDetection::stsSD(observedCases = dataset_1$NumValue,
                                               studyPeriod = dataset_1$StudyPeriod,
                                               timeUnit = input$unit,
                                               startYM = c(
                                                 as.numeric(format(as.Date(input$daterange[1], "%Y-%m-%d"), "%Y")),
                                                 as.numeric(format(as.Date(input$daterange[1], "%Y-%m-%d"), "%m"))
                                                 )
                                               )
      
      #-------------------------------------------------------
      #---- Detection algorithm
      #-------------------------------------------------------
      
      dataset.algo <- EpiSignalDetection::algoSD(dataset.sts,
                                                 algo = input$algo,
                                                 timeUnit = input$unit,
                                                 testingPeriod = input$testingperiod)
      
      
      #-------------------------------
      #--- Incrementation of the Result table
      #------------------------------- 
      
      if(input$algo == "FarringtonFlexible") {
        for(l in 1:(input$testingperiod)){
          Result <- rbind(Result,
                          data.frame(Time = TestingPeriod[input$testingperiod +1 -l],
                                     Place = country,
                                     Stratum = stratum,
                                     Observed = as.character(dataset.algo@observed[l]),
                                     Threshold.ALGO = as.character(round(dataset.algo@upperbound[l],0)),
                                     ALGO = ifelse(dataset.algo@alarm[l],
                                                   "<span style=\"color:#DD4814\">Signal</span>",
                                                   "no"),
                                     Ranking = round(dataset.algo@control$score[l], 2 ),
                                     p.value = ifelse(dataset.algo@control$pvalue[l] < 0.00001,
                                                      "<0.00001", 
                                                      as.character( round(dataset.algo@control$pvalue[l],5)))
                          )
          )
        }
      }
      
      if(input$algo == "GLRNB") {
        
        # --- Special treat for GLRNB because:
        # --- Exceedance score and pvalue are not available in surveillance 1.16.2
        # --- for GLRNB function.
        # --- Need to compute expected number of cases and  exeedance score:
        observed <- dataset.algo@observed
        expected <- dataset.algo@control$mu0
        threshold <- dataset.algo@upperbound
        ranking <- ((observed - expected) / (threshold - expected))
        pvalue <- "Not applicable"
        # ---
        
        for(l in 1:(input$testingperiod)){
          Result <- rbind(Result,
                          data.frame(Time = TestingPeriod[input$testingperiod +1 -l],
                                     Place = country,
                                     Stratum = stratum,
                                     Observed = as.character(observed[l]),
                                     Threshold.ALGO = as.character(round(threshold[l],0)),
                                     ALGO = ifelse(dataset.algo@alarm[l],
                                                   "<span style=\"color:#DD4814\">Signal</span>",
                                                   "no"),
                                     Ranking = round(ranking[l], 2 ),
                                     p.value = pvalue
                          )
          )
        }
      }
      

    }
    
  }
}

Result <- Result[-1,]

```


`r paste(out, collapse='\n')`





## By geographical level


```{r AlarmTableByGeo, results = 'hide', fig.show = 'hide'}

out=NULL

for(i in countries){  
  Result_c <- dplyr::filter(Result, Place == i & grepl("Signal", ALGO))
  row.names(Result_c) <- NULL
  names(Result_c) <- c(paste("Time ( by ", tolower(input$unit), ")", sep = ""),
                       "Place",
                       "Stratum",
                       "Reported cases",
                       "Threshold value",
                       "Signal",
                       "Exceedance score",
                       "P.value")
  
  
  out <- c(out,knitr::knit_child('subsection.Rmd'))
  
}


```


`r paste(out, collapse='\n')`





## By stratification level


```{r AlarmTableByPop, results = 'hide', fig.show = 'hide'}

out=NULL

for(i in strata){  
  Result_c <- dplyr::filter(Result, Stratum == i & grepl("Signal", ALGO))
  row.names(Result_c) <- NULL
  names(Result_c) <- c(paste("Time ( by ", tolower(input$unit), ")", sep = ""),
                       "Place",
                       "Stratum",
                       "Reported cases",
                       "Threshold value",
                       "Signal",
                       "Exceedance score",
                       "P.value")
  
  out <- c(out,knitr::knit_child('subsection.Rmd'))
  
}

```


`r paste(out, collapse='\n')`




